---
title: "README"
author: "Paul van der Kooy"
date: "10/3/2016"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# National Flag test

## Data Product

### Assignment Coursera model Developing Data Products

This repository contains the code for an R and Shiny application to test your knowledge 
of national flags around the world. Results of participants are captured and presented with your own score.  
Assignment for the Building Data Products module of the Data Sciences Specialisation

Content:  
*   README.md  
*   Server.R        (Application server)  
*   UI.R            (Application User Interface)  
*   FlagQuiz.Rpres  (Slidify documentation)  

### Data Sources

This application make use of the open country data information from <http://www.geonames.org/>. It utilizes the country index and the flag repository.  
Example:

```{r}
library(png)
library(RCurl)
country <- "US"
url <- paste0("http://www.geonames.org/flags/m/",tolower(as.character(country)),".png")
img <- readPNG(getURLContent(url))
plot.new()
rasterImage(img,0,0,0.25,0.25)
```

### Application manual

The application is straight forwards and self-explanatory. The user is asked to enter a number of questions he or she likes to answer and a level of difficulty. After confirmation the application presents a number of national flags, which the users has to identify by means of multiple choice questions.  
Finally, the score is maintained and presented back to the user.

### Issues & Regrets

Due to time constraints not all functionality intended has been included.  
1.  The reactivity of the application is not flawless and can be improved  
2.  Collecting statistics from all users and present individual score against the score distribution of the population was not yet realised  
3.  The application was intended to also include Hints  

